Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-08-29 Manuscript/manuscript.Rmd
Fix sampling methods

where $C_{min}$ denotes the set of TAD boundary regions and $C_{maj}$ denotes the set non-TAD boundary regions. CI of heavily imbalanced classes approaches 0, while CI for balanced classes approaches 0.50. To assess the effect of CI on predictive performance, we first used the data with **No Sampling**, that is, the majority and minority classes were used as is. We evaluated three re-sampling techniques. For **Random Under-Sampling (RUS)**, all of the data points from the minority class of the training set were used. Then sampling without replacement was used to obtain the same number of data points from the majority class. For **Random Over-Sampling (ROS)**, all of the data points from the majority class of the training set were used. Then, sampling with replacement from minority class was used to obtain the same number of data points as in the majority class. Lastly, for **SMOTE** (Synthetic Minority Over-Sampling Technique), both random under- and over-sampling was incorporated [@chawla2002smote]. Under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the minority class. The minority class was over-sampled by taking each minority class sample and introducing synthetic examples along the feature vectors joining any/all of the k=5 (default) minority class nearest neighbors. The SMOTE algorithm can have many variations in the weighting of over- and under-sampling. In this study we restricted the algorithm to 100% over-sampling and 200% under-sampling. That is, 1 new synthetic observation was to be created for each existing minority class data point, while 2 data points were simultaneously randomly selected from the majority class. This combination results in perfectly balanced classes. The *DMwR* R package was used to perform SMOTE (version 0.4.1).

[??? Stopped here]

>>>>

where $C_{min}$ denotes the set of TAD boundary regions and $C_{maj}$ denotes the set non-TAD boundary regions. CI of heavily imbalanced classes approaches 0, while CI for balanced classes approaches 0.50. To assess the effect of CI on predictive performance, we first used the data with **No Sampling**, that is, the majority and minority classes were used as is. We evaluated three re-sampling techniques. For **Random Under-Sampling (RUS)**, the majority class was sampled without replacement to obtain the same number of data points in the minority class. For **Random Over-Sampling (ROS)**, the minority class was sampled with replacement to obtain the same number of data points in the majority class. For **SMOTE** (Synthetic Minority Over-Sampling Technique), under-sampling was performed without replacement from the majority class, while over-sampling was performed by creating new synthetic observations using the $k=5$ minority class nearest neighbors [@chawla2002smote] (implemented in the `DMwR` v.0.4.1 R package). We restricted the algorithm to 100% over-sampling and 200% under-sampling, which creates perfectly balanced classes.
